Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-16 surfaces-write-up/surface-write-up.tex
fixed equation names
surfaces: first writing of veronese remark

\ssec{One Hypersurface on Projective Space}
\label{ssec:proj-one-point}

\begin{rem}
\label{rem:proj-veronese}
Remark about how we can assume divisor only consists of hyperplanes
by taking the Veronese embedding.
\todo{write}
\end{rem}

@@

\begin{thm}
\label{thm:proj-effective}
Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i H_i$, with $\alpha_i =
\frac{p_i}{q_i} \in \bq$ and each $H_i$ a hypersurface of
$\bp^m$, be an effective divisor on $\bp^m$.

@@

\begin{lem}\label{P-m-relations-psi}
$\ker(\psi)$ is generated in degree less than
\[
	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
\]
\end{lem}
\begin{proof}
We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
\begin{equation}\label{eqn:relations-psi}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

@@

\begin{proof}
We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
\begin{equation}\label{eqn:relations-psi}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

>>>>

\ssec{Effective Divisors of Hypersurfaces on Projective Space}
\label{ssec:proj-one-point}

\begin{rem}
\label{rem:proj-veronese}
For any divisor $D = \sum_{i = 0}^{n} \alpha_i C_i$ on $\bp^m$
with each $C_i$ a hypersurface, we can use the Veronese mappings
to view $D$ as a divisor on $\bp^{m'}$ for some $m' \in \bz_{\geq 0}$
with $D = \sum_{i = 0}^{n} \alpha_i H_i$ where $H_i$ are hypersurfaces
in $\bp^{m'}$.
\end{rem}

@@

\begin{thm}
\label{thm:proj-effective}
Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
$\bp^m$. Let $D = \sum_{i = 1}^{n} \alpha_i C_i$, with $\alpha_i =
\frac{p_i}{q_i} \in \bq$ and each $C_i$ a hypersurface of
$\bp^m$, be an effective divisor on $\bp^m$.

@@

\begin{lem}\label{P-m-relations-psi}
$\ker(\psi)$ is generated in degree less than
\[
	\frac{\max_{1\le i \le n}(\bida_i)}{\deg(D)} +  \sum_{i=1}^n \ell_i a_i.
\]
\end{lem}
\begin{proof}
We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
\begin{equation}\label{eqn:relations-psi-P-n}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}

@@

\begin{proof}
We first claim that $\psi$ there are $\beta_1, \ldots, \beta_n$ such that $\psi$ has relations of the form
\begin{equation}\label{eqn:relations-psi-hirz}
	(z_i - \beta_i)\prod_{j=1}^n {z_j}^{c_{j}}
\end{equation}
